---
title: "SAS Project"
date: "`r format(Sys.time(), '%X %d %B, %Y')`"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

## cleaning of dataset

```{r}
speed_dating <- read.csv("Speed Dating Data.csv")
head(speed_dating)

req_columns_p <- c("dec_o", "attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1", "shar1_1" ,"imprace" , "imprelig")

req_columns_s <- c("dec", "attr", "sinc", "intel", "fun", "amb", "shar" ,"like")

req_speed_dating_p <- speed_dating[,req_columns_p]
req_speed_dating_s <- speed_dating[,req_columns_s]

head(req_speed_dating_p)
head(req_speed_dating_s)

# to check for the NAs in the dataset  
sum(is.na(req_speed_dating_p))
sum(is.na(req_speed_dating_s))

# to remove all the rows if any column has NA in it.  
req_speed_dating_p <- na.omit(req_speed_dating_p)
req_speed_dating_s <- na.omit(req_speed_dating_s)

req_speed_dating_s$dec <- as.factor(req_speed_dating_s$dec)
req_speed_dating_p$dec_o <- as.factor(req_speed_dating_p$dec_o)

```


## dividing the dataset into training and test set for subject

```{r}
set.seed(1) 
s <- sample(nrow(req_speed_dating_s), round(.5*nrow(req_speed_dating_s)))
train_req_speed_dating_s <- req_speed_dating_s[s,]
test_req_speed_dating_s <- req_speed_dating_s[-s,]
```


## creating a model using training dataset

```{r}
log_reg_model_s <- glm(dec ~ ., data = train_req_speed_dating_s, family = binomial("logit"),maxit = 100)
summary(log_reg_model_s)

```



## testing the model with our traing dataset

```{r}
pred_s <- predict(log_reg_model_s, train_req_speed_dating_s, type="response")
train_bin_preds_s <- as.numeric(pred_s >= 0.5)
train_accuracy_s <- mean(train_bin_preds_s != train_req_speed_dating_s["dec"])
train_accuracy_s
table(train_bin_preds_s, train_req_speed_dating_s$dec)
```




## testing the model with our testing dataset

```{r}
test_preds_s <- predict(log_reg_model_s, test_req_speed_dating_s, type="response")
test_bin_preds_s <- as.numeric(test_preds_s >= 0.5)
test_accuracy_s <- mean(test_bin_preds_s==test_req_speed_dating_s["dec"])
test_accuracy_s
table(test_bin_preds_s, test_req_speed_dating_s$dec)

pred <- predict(log_reg_model_s,test_req_speed_dating_s)$class
table(test_req_speed_dating_s$dec, pred)
mean(test_req_speed_dating_s$dec != pred)

```




## dividing the dataset into training and test set for participants

```{r}
set.seed(1) 
p <- sample(nrow(req_speed_dating_p), round(.5*nrow(req_speed_dating_p)))
train_req_speed_dating_p <- req_speed_dating_p[p,]
test_req_speed_dating_p <- req_speed_dating_p[-p,]
```


## creating a model using training dataset

```{r}
log_reg_model_p <- glm(dec_o ~ ., data = train_req_speed_dating_p, family = binomial("logit"),maxit = 100)
summary(log_reg_model_p)

```



## testing the model with our traing dataset

```{r}
pred_p <- predict(log_reg_model_p, train_req_speed_dating_p, type="response")
train_bin_preds_p <- as.numeric(pred_p >= 0.5)
train_accuracy_p <- mean(train_bin_preds_p != train_req_speed_dating_p["dec_o"])
train_accuracy_p
table(train_bin_preds_p, train_req_speed_dating_p$dec_o)
```


## testing the model with our testing dataset

```{r}
test_preds_p <- predict(log_reg_model_p, test_req_speed_dating_p, type="response")
test_bin_preds_p <- as.numeric(test_preds_p >= 0.5)
test_accuracy_p <- mean(test_bin_preds_p==test_req_speed_dating_p["dec_o"])
test_accuracy_p
table(test_bin_preds_p, test_req_speed_dating_p$dec_o)
```


## forward and backward regression and stepwise

```{r}
step(glm(dec_o~.,data= req_speed_dating_p, family = binomial("logit"),maxit = 100),direction="backward")


step(glm(dec~.,data= req_speed_dating_s, family = binomial("logit"),maxit = 100),direction="backward")
```

